Data Archiving Attitudes

### 2015-05-17 analysis.Rmd
Updated question codebook.

---
title: "Data Archiving Attitudes"
author: Heather Piwowar, Pavel Logacev, Todd J. Vision
date: "May 17, 2015"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
    keep_md: yes
  word_document:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  md_document:
    variant: markdown_github
<!-- csl: apa.csl -->
bibliography: bibliography.bib
---

```{r setup, echo=FALSE, include=TRUE}
suppressPackageStartupMessages({
  require(dplyr)
  require(knitr)
  require(RColorBrewer)
})
```

@@

The survey was carried out using [Survey Monkey](www.surveymonkey.com). Invitations to participate were sent out to $n$ <!-- TODO: how many? -->
authors by email every month. The average non-response rate was $p$. <!-- TODO: response/non-response rates -->

```{r, message=FALSE,  echo=FALSE, fig.width=5, fig.height=3, fig.cap="Number of invitations and responses by quarter."}
library(ggplot2)
library(dplyr)

@@

## Critical questions

>>>>

---
title: "Data Archiving Attitudes"
author: "Heather Piwowar, Pavel Logacev, Todd J. Vision"
date: "May 17, 2015"
output:
  html_document:
    css: style.css
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
  md_document:
    variant: markdown_github
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
bibliography: bibliography.bib
<!-- csl: apa.csl -->
---

```{r setup, echo=FALSE, include=TRUE}
suppressPackageStartupMessages({
  require(dplyr)
  require(knitr)
  require(RColorBrewer)
  require(knitr)
  #require(kfigr)
  opts_chunk$set(message=FALSE, warning=FALSE)
})
#knit_hooks$set(plot = function(x, options) {
#   paste('<figure><img src="',
#         opts_knit$get('base.url'), paste(x, collapse = '.'),
#         '"><figcaption>', options$fig.cap, '</figcaption></figure>',
#         sep = '')
#})

#knit_hooks$set(plot = function(x, options) {
#   paste0('<figure><img src="',opts_knit$get('base.url'), paste(x, collapse = '.'),'">',
#          '<figcaption>', options$fig.cap, '</figcaption></figure>')
#})
```

@@

The survey was carried out using [Survey Monkey](www.surveymonkey.com). Invitations to participate were sent out to $n$ <!-- TODO: how many? -->
authors by email every month. The average non-response rate was $p$. <!-- TODO: response/non-response rates -->
Figure 1 shows the numbers of invitations and responses by the date of the author's last publication.

Participants filled in a questionnaire consisting of 15 questions, most of which were multiple-choice.

```{r responseRates, cache=FALSE, message=FALSE,  echo=FALSE, fig.width=5, fig.height=3, anchor="figure", fig.cap="Number of invitations and responses by quarter."}
library(ggplot2)
library(dplyr)

@@
